---
title: "Scatter Plots with scat_lin_cor"
author: "Bowen Xiao"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Scatter Plots with Correlation Coefficients Using bxfun}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

This vignette demonstrates how to use the `scat.lin.cor` function from the `bxfun` package to create scatter plots with correlation coefficients and optional Bayes Factors. We'll use the built-in `mtcars` dataset for this example.

# Example: Visualizing Relationships in `mtcars`

The `mtcars` dataset includes information on various car models, including their fuel efficiency (`mpg`) and horsepower (`hp`).

First, load the `bxfun` package and the required libraries:

```{r}
# Load libraries
library(bxfun)
library(ggplot2)

# Load the dataset
data("mtcars")
```

```{r}
# Deal with variables
mtcars$hp_inv<-1/mtcars$hp
mtcars$mpg<-scale2num(mtcars$mpg)
mtcars$hp<-scale2num(mtcars$hp)

# Create scatter plot with correlation
scat.lin.cor(mtcars,"mpg","hp",refline = T,BF=T,ci=F,
             xlab = "z-scored miles per gallon",
             ylab = "z-scored horsepower")
```
